State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-06-05 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
updating figurs

\caption{Distribution of the parameters estimates over 250

@@

\subfigure[$\zeta$ convergence]{\includegraphics[width=1.5in]{./Graph/ZetaConvergence.pdf}}
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta0Convergence.pdf}}\\
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta1Convergence.pdf}}
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta2Convergence.pdf}}

@@

\begin{figure*}
\subfigure[][]{\includegraphics{./Graph/KernelEstimate.pdf}}
\subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT.pdf}}\\
\caption{Results for connectivity estimate. In all the subplots the true kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dashed line and the 95~\% confidence interval is shown by the shaded grey region. \textbf{a.} Comparison of kernel estimates to true kernel in the spatial domain. \textbf{b.} Comparison of the true kernel to the estimated kernel in the frequency domain. \dean{Note: needs to be changed to absolute values if we include it.} \dean{Note: Power and dB needs to be non-italicised.}}
\label{fig:KernelEstimates}
\end{figure*}
\begin{figure}[th]
\subfigure[][]{\includegraphics{./Graph/theta0_theta1_ratio.pdf}}
\subfigure[][]{\includegraphics{./Graph/theta0_theta2_ratio.pdf}}\\
\caption{Distribution of the connectivity kernel basis function parameter ratios over 250 realisations. \textbf{a.} The absolute value of the ratio of the local excitatory parameter to the surround inhibition parameter (true ratio is 1.25). \textbf{b.} The ratio of the local excitatory parameter to the longer range excitatory parameter (true ratio is 20).}
\end{figure}
\label{fig:ParametersRatio}
\begin{figure}[th]
\centering
\subfigure[][]{\label{fig:FieldFFT}\includegraphics[scale=0.9]{./Graph/FFTTrueField.pdf}}
\subfigure[][]{\label{fig:EstimatedFieldFFT}\includegraphics[scale=0.9]{./Graph/FFTEstimatedField.pdf}}\\
\caption{Spatial frequency of the neural fields. \textbf{a.} The average (over time) spatial frequency of the neural field. \textbf{b.} The average (over time) spatial frequency of the estimated neural field resulting from the basis function decomposition. As a result of the band limiting properties of the sensors and basis functions the reconstructed shows a narrower bandwidth.}
\label{fig:FFTTrueEstimate}
\end{figure}

  \begin{figure}
   	\begin{center}
   		\includegraphics{./Graph/MRMSE.pdf} 
   	\end{center}
   	\caption{The mean of average RMSE of the estimated field over 250 realisations (solid line) and the 95~\% confidence interval (grey region). \dean{David suggested for us to use percentage error, and use a hard threshold of points close to zero to stop problems with divide by zeros. Also, it might be good to show the data points along the line, so we can see the number of iterations it takes to stabilise.}} 
\label{fig:RMSE}
   \end{figure}
\begin{figure*}[!th]
\centering 
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/TrueField90.pdf}}
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/EstimatedField90.pdf}}
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/EstimationError90.pdf}}\\
\caption{Examples of the neural fields. \textbf{a.} The true field from the non-reduced model the was used to generate data. \textbf{b.} The reconstructed estimated field of the reduced model. \textbf{c.} The absolute error between the true and reconstructed fields.}
\label{fig:FieldEstimate}
\end{figure*}

>>>>

\caption{\parham{caption should be changed}Distribution of the parameters estimates over 100

@@

\subfigure[]{\includegraphics[scale=0.7]{./Graph/ZetaConvergence.pdf}}
\subfigure[][]{\includegraphics[scale=0.7]{./Graph/theta0Convergence.pdf}}\\
\subfigure[][]{\includegraphics[scale=0.7]{./Graph/theta1Convergence.pdf}}
\subfigure[][]{\includegraphics[scale=0.7]{./Graph/theta2Convergence.pdf}}

@@

\begin{figure*}
\subfigure[][]{\includegraphics{./Graph/KernelEstimate.pdf}}
\subfigure[][]{\includegraphics{./Graph/KernelEstimateFFT.pdf}}\\
\caption{Results for connectivity estimate. In all the subplots the true kernel is shown by the solid line, the mean kernel estimate (over 100 realisations) is shown by the dashed line and the 95~\% confidence interval is shown by the shaded grey region. \textbf{a.} Comparison of kernel estimates to true kernel in the spatial domain. \textbf{b.} Comparison of the true kernel to the estimated kernel in the frequency domain. \dean{Note: needs to be changed to absolute values if we include it.} \dean{Note: Power and dB needs to be non-italicised.}}
\label{fig:KernelEstimates}
\end{figure*}
\begin{figure}[th]
\subfigure[][]{\includegraphics{./Graph/theta0_theta1_ratio.pdf}}
\subfigure[][]{\includegraphics{./Graph/theta0_theta2_ratio.pdf}}\\
\caption{Distribution of the connectivity kernel basis function parameter ratios over 100 realisations. \textbf{a.} The absolute value of the ratio of the local excitatory parameter to the surround inhibition parameter (true ratio is 1.25). \textbf{b.} The ratio of the local excitatory parameter to the longer range excitatory parameter (true ratio is 20).}
\end{figure}
\label{fig:ParametersRatio}
\begin{figure}[th]
\centering
\subfigure[][]{\label{fig:FieldFFT}\includegraphics[scale=0.9]{./Graph/FFTTrueField.pdf}}
\subfigure[][]{\label{fig:EstimatedFieldFFT}\includegraphics[scale=0.9]{./Graph/FFTEstimatedField.pdf}}\\
\caption{Spatial frequency of the neural fields. \textbf{a.} The average (over time) spatial frequency of the neural field. \textbf{b.} The average (over time) spatial frequency of the estimated neural field resulting from the basis function decomposition. As a result of the band limiting properties of the sensors and basis functions the reconstructed shows a narrower bandwidth.}
\label{fig:FFTTrueEstimate}
\end{figure}

  \begin{figure}
   	\begin{center}
   		\includegraphics{./Graph/MRMSE.pdf} 
   	\end{center}
   	\caption{The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region). \dean{David suggested for us to use percentage error, and use a hard threshold of points close to zero to stop problems with divide by zeros. Also, it might be good to show the data points along the line, so we can see the number of iterations it takes to stabilise.}} 
\label{fig:RMSE}
   \end{figure}
\begin{figure*}[!th]
\centering 
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/TrueField90.pdf}}
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/EstimatedField90.pdf}}
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/EstimationError90.pdf}}\\
\caption{Examples of the neural fields. \textbf{a.} The true field from the non-reduced model the was used to generate data. \textbf{b.} The reconstructed estimated field of the reduced model. \textbf{c.} The absolute error between the true and reconstructed fields.}
\label{fig:FieldEstimate}
\end{figure*}
